---
title: "Paper 3 Data Analysis"
author: "Tracy Lam-Hine"
date: "5/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r}
library(tidyverse)
library(survey)
library(jtools)
library(janitor)
library(scales)
library(mitools)
library(Hmisc)
library(MASS)
library(boot)
library(parallel)
library(tikzDevice)
```

# Set seed to make results replicable
```{r}
set.seed(123)
```

# Get model and data.frame for stochastic interventions
```{r}
# set model to use
model <- mi_res.anx

# remove latino and other race participants for the model
ah_nlo <- ah_cc %>% 
   filter(latino != 1, 
          multi_1 != "Other_alone") %>% 
   dplyr::select(-c("latino", "preg_w4")) %>% 
  #mutate(multi_1 = fct_relevel(multi_1, "Asian_alone")) %>% 
  mutate(multi_1 = droplevels(multi_1)) %>% 
   filter(complete.cases(.)) # drop incomplete cases for now

# additionally remove pregnant participants for the model
ah_nlop <- ah_cc %>% 
   filter(latino != 1, 
          multi_1 != "Other_alone",
          preg_w4 != 1) %>% 
   dplyr::select(-c("latino", "preg_w4")) %>% 
  mutate(multi_1 = fct_relevel(multi_1, "Asian_alone"),
         multi_1 = droplevels(multi_1)) %>% 
   filter(complete.cases(.)) # drop incomplete cases for now
```

## Intervention 1 IF WHITES ARE REFERENCE
```{r}
si.1 <- function(model, design, df, resamp) {

  # set the level of variation around the mean white ACE score (Poisson dist)
  mean_pois <- tidy.MIresult(MIcombine(with(
    ah_nlo.mi,
    svyby(~ ace_otero, by = ~ multi_1, svymean, data = ah_nlo)
  )))[1, 2]
  
  # get coefficients and vcov matrix from multiply imputed data
  b <- model$coefficients
  vc <- model$variance
  
  # resampling the distributions of the betas n=resamp times
  b.resamp <- MASS::mvrnorm(n = resamp, mu = b, Sigma = vc)
  
  # Create containers for simulated & resampled risk differences
  # RENAMING TO RESAMP.RD.* (BOOTSTRAP HAS SPECIFIC MEANING)
  resamp.rd.wt <- rep(NA, resamp)
  resamp.rd.bl <- rep(NA, resamp)
  resamp.rd.as <- rep(NA, resamp)
  resamp.rd.ai <- rep(NA, resamp)
  resamp.rd.mr <- rep(NA, resamp)
  
  
  # initialize storage vectors for resampled and intervened scores
  acediff.ot.wt <-
    acediff.ot.bl  <- acediff.ot.as <- acediff.ot.ai <-
    acediff.ot.mr <- list()
  acediff.cf.wt <-
    acediff.cf.bl  <- acediff.cf.as <- acediff.cf.ai <-
    acediff.cf.mr <- list()
  
  # storage vector for counts of participants by race across resampled datasets
  obs_resamp <- list()
  
  
  for (b in 1:resamp) {
    index <- sample(nrow(df), replace = T) # same size as cc data
    data.resamp0 <- df[index,]
    
    # observed distribution of covariates: prevalence under no intervention
    
    X.0 <- model.matrix(
      ~ BIO_SEX4 + age_w4 + max_par_edu_w1 + fam_inc_w1 +
        par_sup_w1 + nei_dis_w1 + ace_otero * multi_1,
      data = data.resamp0
    )
    
    # estimate prevalence in original data
    # THIS SHOULDN'T CHANGE IN THE INTERVENTION LOOP:
    p0.wt <- plogis(X.0[X.0[, 11] == 0 &
                          X.0[, 12] == 0 &
                          X.0[, 13] == 0 &
                          X.0[, 14] == 0, ] %*% b.resamp[b, ])
    p0.bl <- plogis(X.0[X.0[, 11] == 1, ] %*% b.resamp[b, ])
    p0.as <- plogis(X.0[X.0[, 12] == 1, ] %*% b.resamp[b, ])
    p0.ai <- plogis(X.0[X.0[, 13] == 1, ] %*% b.resamp[b, ])
    p0.mr <- plogis(X.0[X.0[, 14] == 1, ] %*% b.resamp[b, ])
    # COEFFICIENT VARIES OVER RESAMPLED VALUES
    
    
    # create lists to hold sim results from multiple intervention draws
    simres.ot.wt <-
      simres.ot.bl <- simres.ot.as <- simres.ot.ai <-
      simres.ot.mr <- list()
    simres.cf.wt <-
      simres.cf.bl <- simres.cf.as <- simres.cf.ai <-
      simres.cf.mr <- list()
    
    
    # make a copy of X.0 and data.resamp and identify those receiving intervention
    data.resamp1 <- data.resamp0
    data.resamp1 <- data.resamp1 %>%
      mutate(
        # this is the new exposure variable copied from existing:
        ace_cf = ace_otero,
        # indicator variable for participants receiving intervention
        mod_cf = NA_real_,
        mod_cf = case_when(multi_1 != "White_alone" ~ 1,
                           TRUE ~ 0)
      )
    
    # get IDs of participants who receive intervention
    ids <-
      unique(data.resamp1$AID[data.resamp1$mod_cf == 1])
    
    # stochastic intervention: alter exposure distributions
    
    ### Create a vector of mean_pois with # of obs = ids.
    ### exp(b1 + b2*w1 + b3*w2....) - coming out of data.resamp1
    
    for (j in ids) {
      data.resamp1$ace_cf[data.resamp1$AID == j] <-
        min(10, rpois(1, mean_pois))
    }
    
    # new distribution of covars under intervention scenario
    # call in data.resamp1 and new exposure distribution
    X.1 <-
      model.matrix(
        ~ BIO_SEX4 + age_w4 + max_par_edu_w1 + fam_inc_w1 +
          par_sup_w1 + nei_dis_w1 + ace_cf * multi_1,
        data = data.resamp1
      )
    
    # estimate prevalence under intervention data:
    p1.wt <- plogis(X.1[X.1[, 11] == 0 &
                          X.1[, 12] == 0 &
                          X.1[, 13] == 0 &
                          X.1[, 14] == 0, ] %*% b.resamp[b, ])
    p1.bl <-
      plogis(X.1[X.1[, 11] == 1, ] %*% b.resamp[b, ])
    p1.as <-
      plogis(X.1[X.1[, 12] == 1, ] %*% b.resamp[b, ])
    p1.ai <-
      plogis(X.1[X.1[, 13] == 1, ] %*% b.resamp[b, ])
    p1.mr <-
      plogis(X.1[X.1[, 14] == 1, ] %*% b.resamp[b, ])
    
    # RISK DIFFERENCES FOR EACH OBS IN SAMPLED POPULATION
    rd.wt <- p1.wt - p0.wt
    rd.bl <- p1.bl - p0.bl
    rd.as <- p1.as - p0.as 
    rd.ai <- p1.ai - p0.ai 
    rd.mr <- p1.mr - p0.mr
    
    # FILL IN LIST WITH THE RESAMPLED RISK DIFFERENCES
    resamp.rd.wt[b] <- mean(rd.wt)
    resamp.rd.bl[b] <- mean(rd.bl)
    resamp.rd.as[b] <- mean(rd.as)
    resamp.rd.ai[b] <- mean(rd.ai)
    resamp.rd.mr[b] <- mean(rd.mr)
    
    # get original and intervened aces scores counts 
    sim.ot.wt <-
      data.resamp1 %>% filter(multi_1 == "White_alone") %>%
      group_by(ace_otero) %>% tally()
    sim.ot.bl <-
      data.resamp1 %>% filter(multi_1 == "Black_alone") %>%
      group_by(ace_otero) %>% tally()
    sim.ot.as <-
      data.resamp1 %>% filter(multi_1 == "Asian_alone") %>%
      group_by(ace_otero) %>% tally()
    sim.ot.ai <-
      data.resamp1 %>% filter(multi_1 == "AI/NA_alone") %>%
      group_by(ace_otero) %>% tally()
    sim.ot.mr <-
      data.resamp1 %>% filter(multi_1 == "Multiracial") %>%
      group_by(ace_otero) %>% tally()
    sim.cf.wt <-
      data.resamp1 %>% filter(multi_1 == "White_alone") %>%
      group_by(ace_cf) %>% tally()
    sim.cf.bl <-
      data.resamp1 %>% filter(multi_1 == "Black_alone") %>%
      group_by(ace_cf) %>% tally()
    sim.cf.as <-
      data.resamp1 %>% filter(multi_1 == "Asian_alone") %>%
      group_by(ace_cf) %>% tally()
    sim.cf.ai <-
      data.resamp1 %>% filter(multi_1 == "AI/NA_alone") %>%
      group_by(ace_cf) %>% tally()
    sim.cf.mr <-
      data.resamp1 %>% filter(multi_1 == "Multiracial") %>%
      group_by(ace_cf) %>% tally()
    
    # FILL IN LIST FOR SCORES FROM INTERVENTIONS ACROSS b RESAMPLED DATASETS
    acediff.ot.wt[[b]] <- sim.ot.wt
    acediff.ot.bl[[b]] <- sim.ot.bl
    acediff.ot.as[[b]] <- sim.ot.as
    acediff.ot.ai[[b]] <- sim.ot.ai
    acediff.ot.mr[[b]] <- sim.ot.mr
    acediff.cf.wt[[b]] <- sim.cf.wt
    acediff.cf.bl[[b]] <- sim.cf.bl
    acediff.cf.as[[b]] <- sim.cf.as
    acediff.cf.ai[[b]] <- sim.cf.ai
    acediff.cf.mr[[b]] <- sim.cf.mr
    
    # FILL IN LIST WITH COUNTS OF PARTICIPANTS
    obs_cts <- data.resamp0 %>% group_by(multi_1) %>% tally() %>%
      rename(!!paste0("rs_", b) := n)
    obs_resamp[[b]] <- obs_cts
  }
  
  diffs <- bind_rows(
    bind_rows(
      acediff.ot.wt %>% reduce(full_join, by = "ace_otero") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>%
        dplyr::select(name, ace_ct, n),
      acediff.cf.wt %>% reduce(full_join, by = "ace_cf") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>%
        dplyr::select(name, ace_ct, n)
    ) %>%
      mutate(multi_1 = "White_alone"),
    bind_rows(
      acediff.ot.bl %>% reduce(full_join, by = "ace_otero") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>%
        dplyr::select(name, ace_ct, n),
      acediff.cf.bl %>% reduce(full_join, by = "ace_cf") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>%
        dplyr::select(name, ace_ct, n)
    )  %>%
      mutate(multi_1 = "Black_alone"),
    bind_rows(
      acediff.ot.as %>% reduce(full_join, by = "ace_otero") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n),
      acediff.cf.as %>% reduce(full_join, by = "ace_cf") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n)
    ) %>%
      mutate(multi_1 = "Asian_alone"),
    bind_rows(
      acediff.ot.ai %>% reduce(full_join, by = "ace_otero") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n),
      acediff.cf.ai %>% reduce(full_join, by = "ace_cf") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n)
    ) %>%
      mutate(multi_1 = "AI/NA_alone"),
    bind_rows(
      acediff.ot.mr %>% reduce(full_join, by = "ace_otero") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n),
      acediff.cf.mr %>% reduce(full_join, by = "ace_cf") %>%
        adorn_totals("col") %>% rename("n" = Total) %>%
        pivot_longer(cols = 1, values_to = "ace_ct") %>% dplyr::select(name, ace_ct, n)
    ) %>%
      mutate(multi_1 = "Multiracial")
  ) %>%
    mutate(
      multi_1 =
        case_when(
          multi_1 == "White_alone" ~ "White",
          multi_1 == "Black_alone" ~ "Black",
          multi_1 == "Asian_alone" ~ "Asian",
          multi_1 == "AI/NA_alone" ~ "AI/NA",
          TRUE ~ multi_1
        )
    )
  
  # sum counts of participants across all resampled datasets
  resamp_cts <-
    obs_resamp %>% reduce(full_join, by = "multi_1") %>%
    adorn_totals("col") %>% dplyr::select(multi_1, Total) %>% untabyl() %>%
    mutate(multi_1 = as.character(multi_1),
           multi_1 = str_remove(multi_1, "_alone"))
  
  # calculate mean ace score before and after intervention
  diffs_sum <- diffs %>%
    mutate(sump = ace_ct * n) %>%
    group_by(multi_1, name) %>%
    summarise(sum = sum(sump)) %>%
    pivot_wider(names_from = name, values_from = sum) %>%
    ungroup() %>%
    inner_join(resamp_cts, by = "multi_1") %>%
    mutate(ace_otero_mean = ace_otero / Total,
           ace_cf_mean = ace_cf / Total) %>%
    dplyr::select(multi_1, Total, ace_otero_mean, ace_cf_mean)
  
  
  return(list(
    df.resamp = tibble(
      "white" = resamp.rd.wt,
      "black" = resamp.rd.bl,
      "asian" = resamp.rd.as,
      "ai/na" = resamp.rd.ai,
      "multiracial" = resamp.rd.mr
    ),
    summary = tibble(
      "group" = c("white", "black", "asian", "ai/na", "multiracial"),
      "rd_mean" = c(
        mean(resamp.rd.wt),
        mean(resamp.rd.bl),
        mean(resamp.rd.as),
        mean(resamp.rd.ai),
        mean(resamp.rd.mr)
      ) * 100,
      "rd_med" = c(
        median(resamp.rd.wt),
        median(resamp.rd.bl),
        median(resamp.rd.as),
        median(resamp.rd.ai),
        median(resamp.rd.mr)
      ) * 100,
      "lb" = c(
        quantile(resamp.rd.wt, 0.025),
        quantile(resamp.rd.bl, 0.025),
        quantile(resamp.rd.as, 0.025),
        quantile(resamp.rd.ai, 0.025),
        quantile(resamp.rd.mr, 0.025)
      ) * 100,
      "ub" = c(
        quantile(resamp.rd.wt, 0.975),
        quantile(resamp.rd.bl, 0.975),
        quantile(resamp.rd.as, 0.975),
        quantile(resamp.rd.ai, 0.975),
        quantile(resamp.rd.mr, 0.975)
      ) * 100,
      "se" = c(
        sd(resamp.rd.wt) / sqrt(length(resamp.rd.wt)),
        sd(resamp.rd.bl) / sqrt(length(resamp.rd.bl)),
        sd(resamp.rd.as) / sqrt(length(resamp.rd.as)),
        sd(resamp.rd.ai) / sqrt(length(resamp.rd.ai)),
        sd(resamp.rd.mr) / sqrt(length(resamp.rd.mr))
      )
    ),
    diffs = diffs,
    diffs_sum = diffs_sum
  ))
}

```

## Simulate Intervention 1
```{r}
options(mc.cores = 4)

start <- Sys.time()
si.1_depb_1000 <- si.1(model = mi_rr.depb, design = ah_nlo.mi, df = ah_nlo.mi$designs[[12]]$variables, resamp = 1000)
stop <- Sys.time()

stop-start

```

## Another simulation
```{r}
options(mc.cores = 4)

start <- Sys.time()
si.1_depb_1000 <- si.1(model = mi_depb.ast, design = ah_nlo.mi, df = ah_nlo.mi$designs[[12]]$variables, resamp = 1000)
stop <- Sys.time()

stop-start

```

## GET PLOT OF BASELINE AND INTERVENED ACES DISTRIBUTIONS
```{r}
# plot results
p3_plot <- ggplot(si.1_depb_1000$diffs, aes(x = ace_ct, y = n, fill = name)) +
  geom_bar(stat = "identity",
           alpha = 0.4,
           position = "identity") +
  facet_wrap(vars(multi_1), scales = "free_y", ncol = 2) +
  scale_fill_discrete(name = "ACE Score",
                      labels = c("Intervened", "Baseline")) +
  scale_x_continuous(breaks = c(0:10)) +
  scale_y_continuous(labels = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.title.x = element_blank(),
        legend.position = "bottom") +
  ylab("Count")

# get plots in LaTeX
options(tikzDocumentDeclaration = "\\documentclass[12pt]{article}")

tikz(file = "p3_plot.tex", width = 5.5)

print(p3_plot)

dev.off()
```

## GET PLOT OF SIMULATED RISK DIFFERENCES FROM RESAMPLED DATA
```{r}
si_res <- si.1_depb_1000$df.resamp %>% 
  pivot_longer(cols=c(1:5),names_to = "race") %>% 
  mutate(value = value * 100)

labs <- c("White n =\n(7,758,492)", "Black n =\n(2,919,331)", "Asian n =\n(807,539)", "AI/NA n =\n(76,681)", "Multiracial\nn = (835,957)")

p3_rdplot_depb <- ggplot() + 
  geom_point(data = si_res, 
             aes(x = race, y = value, color = race),
             alpha = 0.3,
             position = position_jitter()) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_x_discrete(limits = c("white", "black", "asian", "ai/na", "multiracial"),
                   labels = labs) +
  scale_y_continuous(breaks=seq(-10,10,by=1)) +
  ylab("Simulated cases of depression averted per 100 population")

  # get plots in LaTeX  
  options(tikzDocumentDeclaration = "\\documentclass[12pt]{article}")  
  
  tikz(file = "p3_rdplot.tex", width = 5.5)
    
  print(p3_rdplot_depb) 
    
  dev.off()
```


## GET PLOT OF SIMULATED ASTHMA RISK DIFFERENCES FROM RESAMPLED DATA
```{r}
si_res_ast <- si.1_ast_1000$df.resamp %>% 
  pivot_longer(cols=c(1:5),names_to = "race") %>% 
  mutate(value = value * 100)

labs <- c("White n =\n(7,758,492)", "Black n =\n(2,919,331)", "Asian n =\n(807,539)", "AI/NA n =\n(76,681)", "Multiracial\nn = (835,957)")

p3_rdplot_ast <- ggplot() + 
  geom_point(data = si_res_ast, 
             aes(x = race, y = value, color = race),
             alpha = 0.3,
             position = position_jitter()) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_x_discrete(limits = c("white", "black", "asian", "ai/na", "multiracial"),
                   labels = labs) +
  scale_y_continuous(breaks=seq(-10,10,by=1)) +
  ylab("Simulated cases of asthma averted per 100 population")
    
  print(p3_rdplot_ast) 
```
## GET PLOT OF SIMULATED ANXIETY RISK DIFFERENCES FROM RESAMPLED DATA
```{r}
si.1_anx_1000 <- si.1(model = mi_rr.anx, design = ah_nlo.mi, df = ah_nlo.mi$designs[[12]]$variables, resamp = 1000)


p3_plot_anx <- ggplot(si.1_anx_1000$diffs, aes(x = ace_ct, y = n, fill = name)) +
  geom_bar(stat = "identity",
           alpha = 0.4,
           position = "identity") +
  facet_wrap(vars(multi_1), scales = "free_y", ncol = 2) +
  scale_fill_discrete(name = "ACE Score",
                      labels = c("Intervened", "Baseline")) +
  scale_x_continuous(breaks = c(0:10)) +
  scale_y_continuous(labels = unit_format(unit = "K", scale = 1e-3)) +
  theme(axis.title.x = element_blank(),
        legend.position = "bottom") +
  ylab("Count")

print(p3_plot_anx)


si_res_anx <- si.1_anx_1000$df.resamp %>% 
  pivot_longer(cols=c(1:5),names_to = "race") %>% 
  mutate(value = value * 100)

labs <- c("White n =\n(7,759,094)", "Black n =\n(2,916,800)", "Asian n =\n(807,663)", "AI/NA n =\n(77,051)", "Multiracial\nn = (837,392)")

p3_rdplot_anx <- ggplot() + 
  geom_point(data = si_res_anx, 
             aes(x = race, y = value, color = race),
             alpha = 0.3,
             position = position_jitter()) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_x_discrete(limits = c("white", "black", "asian", "ai/na", "multiracial"),
                   labels = labs) +
  scale_y_continuous(breaks=seq(-10,10,by=1)) +
  ylab("Simulated cases of anxiety averted per 100 population")
    
  print(p3_rdplot_anx) 
```

## GET PLOT OF SIMULATED SUICIDAL IDEATION RISK DIFFERENCES FROM RESAMPLED DATA
```{r}
si.1_sui_1000 <- si.1(model = mi_rr.sui, design = ah_nlo.mi, df = ah_nlo.mi$designs[[12]]$variables, resamp = 1000)

si_res_sui <- si.1_sui_1000$df.resamp %>% 
  pivot_longer(cols=c(1:5),names_to = "race") %>% 
  mutate(value = value * 100)

labs <- c("White n =\n(7,759,094)", "Black n =\n(2,916,800)", "Asian n =\n(807,663)", "AI/NA n =\n(77,051)", "Multiracial\nn = (837,392)")

p3_rdplot_sui <- ggplot() + 
  geom_point(data = si_res_sui, 
             aes(x = race, y = value, color = race),
             alpha = 0.3,
             position = position_jitter()) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_x_discrete(limits = c("white", "black", "asian", "ai/na", "multiracial"),
                   labels = labs) +
  scale_y_continuous(breaks=seq(-10,10,by=1)) +
  ylab("Simulated cases of suicidal ideation averted per 100 population")
    
  print(p3_rdplot_sui) 
```

## Intervention 2 IF ASIANS ARE REFERENCE
si2 <- function(model, design, df, resamp, sims){
  
     ### I THINK BOOTSTRAP # AND RESAMP SHOULD BE THE SAME (COULD BE MISTAKEN)
     ### SIMS SHOULD BE THE # OF INTERVENTIONS TO DRAW FOR EACH CONFOUNDER SET.
     
     # set the level of variation around the mean white ACE score (Poisson dist)
     mean_pois <- tidy.MIresult(MIcombine(with(
          design,
          svyglm(ace_otero ~ multi_1,
                 data=design,
                 family=quasipoisson())
     )))
     mean_pois <- exp(mean_pois[1,2] + # intercept
                           mean_pois[2,2]) # beta coef for white
     
     # get coefficients and vcov matrix from multiply imputed data
     b <- model$coefficients
     vc <- model$variance
     
     # resampling the distributions of the betas n=resamp times
     b.resamp <- MASS::mvrnorm(n=resamp, mu = b, Sigma=vc)
     
     # Create containers for simulated & resampled risk differences
     # RENAMING TO RESAMP.RD.* (BOOTSTRAP HAS SPECIFIC MEANING)
     resamp.rd.as <- rep(NA, resamp) 
     resamp.rd.wt <- rep(NA, resamp) 
     resamp.rd.bl <- rep(NA, resamp) 
     resamp.rd.ai <- rep(NA, resamp) 
     resamp.rd.mr <- rep(NA, resamp) 
     
     
     for (b in 1:resamp){
          
          index <- sample(nrow(df), replace=T) # same size as cc data
          data.resamp0 <- df[index,]
          
          # observed distribution of covariates: prevalence under no intervention
          
          X.0 <- model.matrix(
               ~ BIO_SEX4 + age_w4 + mis_w1 + max_par_edu_w1 + fam_inc_w1 + 
                    par_sup_w1 + exp_dis_w4 + nei_dis_w1 + ace_otero * multi_1,
               data=data.resamp0
          )
          
          # estimate prevalence of anxiety in original data
          # THIS SHOULDN'T CHANGE IN THE INTERVENTION LOOP:
          p0.as <- plogis(X.0[X.0[, 13] == 0 &
                                   X.0[, 14] == 0 &
                                   X.0[, 15] == 0 &
                                   X.0[, 16] == 0, ] %*% b.resamp[b, ])
          p0.wt <- plogis(X.0[X.0[, 13] == 1, ] %*% b.resamp[b, ])
          p0.bl <- plogis(X.0[X.0[, 14] == 1, ] %*% b.resamp[b, ])
          p0.ai <- plogis(X.0[X.0[, 15] == 1, ] %*% b.resamp[b, ]) 
          p0.mr <- plogis(X.0[X.0[, 16] == 1, ] %*% b.resamp[b, ])
          # COEFFICIENT VARIES OVER RESAMPLED VALUES
          

          # BEST TO CLEAR OUT THESE STORAGE MATRICES HERE:
          rd.wt <- matrix(NA, nrow=length(p0.wt), ncol=sims) # ROW=OBS, COL=DRAW FROM INTERVENTION
          rd.bl <- matrix(NA, nrow=length(p0.bl), ncol=sims)
          rd.as <- matrix(NA, nrow=length(p0.as), ncol=sims)
          rd.ai <- matrix(NA, nrow=length(p0.ai), ncol=sims)
          rd.mr <- matrix(NA, nrow=length(p0.mr), ncol=sims)
          
          
          # INTERVENTION LOOP
          # TO AVERAGE OVER THE RANDOM DISTRIBUTION OF INTERVENTIONS
          for (i in 1:sims){
               # make a copy of X.0 and data.resamp and identify those receiving intervention
               data.resamp1 <- data.resamp0
               data.resamp1 <- data.resamp1 %>%
                    mutate(
                         # this is the new exposure variable copied from existing:
                         ace_cf = ace_otero,
                         # indicator variable for participants receiving intervention
                         mod_cf = NA_real_,
                         mod_cf = case_when(multi_1 != "Asian_alone" ~ 1,
                                            TRUE ~ 0)
                    )
               
               # get IDs of participants who receive intervention
               ids <- unique(data.resamp1$AID[data.resamp1$mod_cf == 1])
               
               # stochastic intervention: alter exposure distributions
               
               ### Create a vector of mean_pois with # of obs = ids. 
               ### exp(b1 + b2*w1 + b3*w2....) - coming out of data.resamp1
               
               for (j in ids){
                    data.resamp1$ace_cf[data.resamp1$AID == j] <- min(10, rpois(1, mean_pois))
               }
               
               # new distribution of covars under intervention scenario
               # call in data.resamp1 and new exposure distribution
               X.1 <- 
                    model.matrix(
                         ~ BIO_SEX4 + age_w4 + mis_w1 + max_par_edu_w1 + fam_inc_w1 + 
                              par_sup_w1 + exp_dis_w4 + nei_dis_w1 + ace_cf * multi_1,
                         data=data.resamp1
                    )
               
               # estimate prevalence of anxiety under intervention data:
               p1.wt <- plogis(X.1[X.1[, 13] == 0 &
                                     X.1[, 14] == 0 &
                                     X.1[, 15] == 0 &
                                     X.1[, 16] == 0, ] %*% b.resamp[b, ]) 
               p1.bl <- plogis(X.1[X.1[, 13] == 1, ] %*% b.resamp[b, ]) 
               p1.as <- plogis(X.1[X.1[, 14] == 1, ] %*% b.resamp[b, ]) 
               p1.ai <- plogis(X.1[X.1[, 15] == 1, ] %*% b.resamp[b, ]) 
               p1.mr <- plogis(X.1[X.1[, 16] == 1, ] %*% b.resamp[b, ]) 
               
               # RISK DIFFERENCES FOR EACH OBS IN SAMPLED POPULATION
               rd.wt[,i] <- p1.wt - p0.wt # EACH (ROW, COLUMN) IS THE RD FOR A OBSERVATION (ROW) FOR A
               rd.bl[,i] <- p1.bl - p0.bl # SPECIFIC RANDOM DRAW (A) FROM INTERVENTION DIST 
               rd.as[,i] <- p1.as - p0.as # AT EACH INTERVENTION DRAW (COLUMN I)
               rd.ai[,i] <- p1.ai - p0.ai # GIVEN COVARIATES W (COL), 
               rd.mr[,i] <- p1.mr - p0.mr # CORRESPONDS TO E[Y|A,W]
                                          
          }
          
          # THE RESAMPLED RISK DIFFERENCE,
          resamp.rd.wt[b] <- mean(rowMeans(rd.wt)) 
          resamp.rd.bl[b] <- mean(rowMeans(rd.bl)) 
          resamp.rd.as[b] <- mean(rowMeans(rd.as)) 
          resamp.rd.ai[b] <- mean(rowMeans(rd.ai)) 
          resamp.rd.mr[b] <- mean(rowMeans(rd.mr)) 
               # rowMeans() GIVES E_{A|W}[E[Y|A,W] - E[Y]] (WILL BE NROW(DF) OF THESE)
               # mean() GIVES E_{W}[-above-] (WILL BE 1 OF THESE FOR EACH LOOP THROUGH RESAMPLE)
     }
     

     return(
       list(
         df.resamp = tibble("white" = resamp.rd.wt,
                            "black" = resamp.rd.bl,
                            "asian" = resamp.rd.as,
                            "ai/na" = resamp.rd.ai,
                            "multiracial" = resamp.rd.mr
                            ), 
         summary = tibble(
           "group" = c("white", "black", "asian", "ai/na", "multiracial"),
           "rd" = c(mean(resamp.rd.wt), mean(resamp.rd.bl), mean(resamp.rd.as), 
                  mean(resamp.rd.ai), mean(resamp.rd.mr))*100,
           "lb" = c(quantile(resamp.rd.wt, 0.025), quantile(resamp.rd.bl, 0.025), 
                    quantile(resamp.rd.as, 0.025), quantile(resamp.rd.ai, 0.025),
                    quantile(resamp.rd.mr, 0.025))*100,
           "ub" = c(quantile(resamp.rd.wt, 0.975), quantile(resamp.rd.bl, 0.975), 
                    quantile(resamp.rd.as, 0.975), quantile(resamp.rd.ai, 0.975),
                    quantile(resamp.rd.mr, 0.975))*100 
           "se" = c(sd(resamp.rd.wt)/sqrt(length(resamp.rd.wt)),
                    sd(resamp.rd.bl)/sqrt(length(resamp.rd.bl)),
                    sd(resamp.rd.as)/sqrt(length(resamp.rd.as)),
                    sd(resamp.rd.ai)/sqrt(length(resamp.rd.ai)),
                    sd(resamp.rd.mr)/sqrt(length(resamp.rd.mr)),
                    )
           )
         )
     )
}



## Simulate Intervention 2

options(mc.cores = 4)

start <- Sys.time()
si_ast <- si(model = mi_res.ast, design = ah_nlo.mi, df = ah_nlo, resamp = 1000, sims = 1000)
stop <- Sys.time()

stop-start

save.image("C:/Users/lamhine/Desktop/env_2022-07-05.RData")